Gravitational wave sources in our Galactic backyard: Predictions for BH and NS binaries in LISA

### 2021-07-06 paper/tex/sections/discussion.tex
clear up caveats

\textit{Eccentricity measurement uncertainty:} As noted in Sec.~\ref{sec:ecc_unc}, the method that we use to determine the eccentricity uncertainty is pessimistic as it requires each harmonic to be individually detectable. In reality this may not be necessary depending on the efficacy of matched-filter analysis of LISA data. For an eccentric source to have been detected within the LISA data, several harmonics would already have to have been matched as the same source. This could be done by looking in the same region of the sky for signals with similar chirp masses and distances to the most detectable harmonic in order to find other harmonics that are below the regular detection threshold. This would allow one to refine the measurement of the eccentricity uncertainty much further by comparing the many different harmonics. Therefore, the eccentricity uncertainty that we calculate in this study is a pessimistic estimate. Smaller eccentricity uncertainties would have two main effects on our results. Firstly, the chirp mass error would decrease slightly in the cases where it is dominated by the eccentricity uncertainty, however it is mainly dominated by the frequency derivative uncertainty since most sources are essentially stationary and so have extremely small chirps. Secondly, it would improve our ability to distinguish between WDWDs and these higher mass DCOs. However, until we know more about how LISA will search for eccentric sources, we rely upon our pessimistic estimates.

>>>>

\textit{Eccentricity measurement uncertainty:} The method that we use to determine the eccentricity uncertainty is pessimistic as it requires each harmonic to be individually detectable \citep[e.g.][]{Lau+2020}. In reality this may not be necessary depending on the efficacy of matched-filter analysis of LISA data. For an eccentric source to have been detected within the LISA data, several harmonics would already have to have been matched as the same source. This could be done by looking in the same region of the sky for signals with similar chirp masses and distances to the most detectable harmonic in order to find other harmonics that are below the regular detection threshold. This would allow one to refine the measurement of the eccentricity uncertainty much further by comparing the many different harmonics. Therefore, the eccentricity uncertainty that we calculate in this study is a pessimistic estimate. Smaller eccentricity uncertainties would have two main effects on our results. Firstly, the chirp mass error would decrease slightly in the cases where it is dominated by the eccentricity uncertainty, however it is mainly dominated by the frequency derivative uncertainty since most sources are essentially stationary and so have extremely small chirps. Secondly, it would improve our ability to distinguish between WDWDs and these higher mass DCOs. However, until we know more about how LISA will search for eccentric sources, we rely upon our pessimistic estimates.
